Moral Foundations of U.S. Political News Organizations

### 2019-04-01 pilot_manuscript.Rmd
almost there i think

```{r exp1 source descriptives, results = 'asis', echo = FALSE, message = F}

@@

@@

@@

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv")
NPR_kav = read.csv("exp2_data/NPR_kav.csv")
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv")
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv")
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv")
FOX_kav = read.csv("exp2_data/FOX_kav.csv")
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv")
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv")
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv")
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv")

#merge it together
overalldata_kav = rbind(NYtimes_kav, NPR_kav)
overalldata_kav = rbind(overalldata_kav, SLATE_kav)
overalldata_kav = rbind(overalldata_kav, HUFFPO_kav)
overalldata_kav = rbind(overalldata_kav, POLITICO_kav)
overalldata_kav = rbind(overalldata_kav, FOX_kav)
overalldata_kav = rbind(overalldata_kav, BREITBART_kav)
overalldata_kav = rbind(overalldata_kav, RUSH_kav)
overalldata_kav = rbind(overalldata_kav, BLAZE_kav)
overalldata_kav = rbind(overalldata_kav, HANNITY_kav)

write.csv(overalldata_kav, "exp2_data/overalldata_kav.csv", row.names = F)

##pull in the data
master_kav = read.csv("exp2_data/overalldata_kav.csv", stringsAsFactors = F)

@@

##all data
final_kav = subset(nodis, URLS == FALSE)

tapply(final_kav$wordcount, final_kav$Source, mean)
tapply(final_kav$wordcount, final_kav$Source, sum)

write.csv(final_kav, "exp2_data/finaldata_kav.csv")
```

```{r data_clean_gs, eval = T, echo = F}
##combine all gs data into one dataset
#read it in
NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv")
NPR_gs = read.csv("exp2_data/NPR_gs.csv")
SLATE_gs = read.csv("exp2_data/SLATE_gs.csv")
HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv")
POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv")
FOX_gs = read.csv("exp2_data/FOX_gs.csv")
BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv")
RUSH_gs = read.csv("exp2_data/RUSH_gs.csv")
BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv")
HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv")

#merge it together
overalldata_gs = rbind(NYtimes_gs, NPR_gs)
overalldata_gs = rbind(overalldata_gs, SLATE_gs)
overalldata_gs = rbind(overalldata_gs, HUFFPO_gs)
overalldata_gs = rbind(overalldata_gs, POLITICO_gs)
overalldata_gs = rbind(overalldata_gs, FOX_gs)
overalldata_gs = rbind(overalldata_gs, BREITBART_gs)
overalldata_gs = rbind(overalldata_gs, RUSH_gs)
overalldata_gs = rbind(overalldata_gs, BLAZE_gs)
overalldata_gs = rbind(overalldata_gs, HANNITY_gs)

write.csv(overalldata_gs, "exp2_data/overalldata_gs.csv", row.names = F)

##pull in the data
master_gs = read.csv("exp2_data/overalldata_gs.csv", stringsAsFactors = F)

@@

##all data
final_gs = subset(nodis, URLS == FALSE)

tapply(final_gs$wordcount, final_gs$Source, mean)
tapply(final_gs$wordcount, final_gs$Source, sum)

write.csv(final_gs, "exp2_data/finaldata_gs.csv")
```

```{r stem_text_both, eval = T, echo = F}
##stem Kav text
final_kav = read.csv("exp2_data/finaldata_kav.csv", stringsAsFactors = F)
#final = na.omit(final) #one weird NA line

#process the Text column (write a loop) - save processed text as a separate column
for(i in 1:nrow(final_kav)) {

@@

##stem GS text
final_gs = read.csv("exp1_data/finaldata_gs.csv", stringsAsFactors = F)

@@

  final_gs$edited[i] = preprocess(fina_gs$Text[i], #one value at a time
           case = "lower", 
           remove.punct = TRUE,
           remove.numbers = FALSE, 
           fix.spacing = TRUE)

@@

```
```{r stem_warriner_exp2, eval = T, echo = F}
##open the Warriner data for later
warriner = read.csv("exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)

>>>>

```{r exp1_source_descriptives, results = 'asis', echo = FALSE, message = F}

@@

####build the table here####
tableprint = matrix(NA, nrow=4, ncol=7)
colnames(tableprint) = c("Sources", "Unique_Words", "stuff")

tableprint[ , 1] = levels(final$Source)
tableprint[ , 2] = tapply(final$uniquewords, final$Source, mean)

#change this to match
apa_table(as.data.frame(tableprint),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Experiment 1 Results - Multilevel Model", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 6))
          )

@@

talk about the table here

@@

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")

#merge it together
master_kav = rbind(NYtimes_kav, NPR_kav, SLATE_kav, 
                        HUFFPO_kav, POLITICO_kav, FOX_kav, 
                        BREITBART_kav, RUSH_kav, BLAZE_kav, 
                        HANNITY_kav)

@@

##take out the disqus ones - there are none
#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]

##all data
final_kav = nozero
```

```{r data_clean_gs, eval = T, echo = F}
##combine all gs data into one dataset
#read it in
NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F)
NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F)
SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F)
HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F)
POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F)
FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F)
BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F)
RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F)
BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F)
HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F)

#merge it together
master_gs = rbind(NYtimes_gs, NPR_gs, SLATE_gs, 
                        HUFFPO_gs, POLITICO_gs, FOX_gs, 
                        BREITBART_gs, RUSH_gs, BLAZE_gs, 
                        HANNITY_gs)

@@

##take out the disqus ones
#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]

##all data
final_gs = nozero
```

```{r stem_text_both, eval = T, echo = F}
#process the Text column (write a loop) - save processed text as a separate column
for(i in 1:nrow(final_kav)) {

@@

@@

  final_gs$edited[i] = preprocess(final_gs$Text[i], #one value at a time
           case = "lower", 
           remove.punct = TRUE,
           remove.numbers = FALSE, 
           fix.spacing = TRUE)

@@
